---
title: "covid 19"
author: "Maryana Maayah"
date: "Fall 2020"
output:
  html_document: default
  pdf_document: default
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
options(digits=2)
require(tidyverse)
require(tigerstats)
require(lubridate)
kRdata <- read.csv(file = 'kRdata.csv')
```
### Data is from the Patient_Info dataset from South Korea 1 Jan to 1 May 
### This is contained in a downloadable zip file from kaggle

$H_0$:no difference between death rate due to covid 19 between men and women   

$H_1$: there is a difference between rate due to covid 19 between men and women

Some data is not gender-coded - the gender should only be male or female
77 of the data entries were genes encoded as null, so we delete them.
Should the patient be alive or dying - we adjust that too 
 
# Question 1 - Is dying independent of sex

## We create two bar charts - one based on frequency and the other on percent


```{r}
barchartGC(~result + sex,data=kRdata)
barchartGC(~result + sex,data=kRdata, type="percent")

```
  
The bar graph shows that more males have died from COVID-19 than females
  
Table of patients:
```{r}
table1 <- xtabs(~result + sex,data=kRdata)
rowPerc(table1)
colPerc(table1)
print(table1)
```

The numerical summary shows the large proportion of males who died among the females


```{r}
chisq.test(table1)
chisqtestGC(table1)
fisher.test(table1)
```

If you are a male a grater 2.3 times then if you are a female
The 95 percent confidence interval is 1.4 to 3.9. This means that more men smoke than females
  
## Conclusions

Death is not independent of gender. Men are more likely than women to die
